Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-08 hotstorage13/main.tex
fix bib refs

\author{
Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, Hong Tang$^\dagger$ \\
{\normalsize$^\star$Department of Computer Science, University of California at Santa Barbara}
  {\normalsize$^\dagger$Alibaba Inc.}
}

@@

%  }%
%  {%
%    \end{oldthebibliography}%
%  }
{\small
\bibliographystyle{abbrv}
\bibliography{library,dedup1}
}
\end{document}

>>>>

\author{
Wei Zhang$^{\star}$, Tao Yang$^\star$, Gautham Narayanasamy$^\star$, Hong Tang$^\dagger$ \\
{\normalsize$^\star$ University of California at Santa Barbara} \ \ \ 
  {\normalsize$^\dagger$Alibaba Inc.}
}

@@

%  }%
%  {%
%    \end{oldthebibliography}%
%  }
{\small
\bibliographystyle{abbrv}
\bibliography{library}
}
\end{document}
